Lens Modeling in \sw

### 2013-09-10 text/tex/abstract.tex
a few words on sl, added bib entries
abstract edited

\begin{abstract}
In Spacewarps, volunteers are invited to search sky surveys for lens
candidates.  Here we report on a system that allows experienced
volunteers to model lens candidates.  A sample of 29 simulated lenses
were modelled, each multiple times.  The quality of the models was
then examined in two ways.  First, the image parities and time
orderings: these were identified correctly in most cases, but not
always.  Second, the mean convergence (equivalent to the enclosed
mass): this was constrained consistently well in the image region.
The performance of professionals and experienced volunteers was
comparable.
\end{abstract}

>>>>

\begin{abstract}
In Spacewarps, volunteers are invited to search sky surveys for lens
candidates.  Here we report on a system that allows experienced
volunteers to model lens candidates.  A sample of 29 simulated lenses
were modelled, each multiple times.  The quality of the models was
then examined in different ways.  In particular, (i)~the image
parities and time orderings were identified correctly in most cases,
but not always; (ii)~the mean convergence (equivalent to the enclosed
mass) was quite well constrained in the image region; (iii)~the
performance of experienced volunteers was comparable to professionals.
\end{abstract}
